% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  11pt,
  a4paper,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\newcommand{\fullwidthrule}{\noindent\rule{\textwidth}{0.4pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={James Wills},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{James Wills}
\author{}
\date{}

\begin{document}
\maketitle

\href{http://linkedin.com/in/jamesjwills}{LinkedIn} \textbar{}
\href{http://jameswills.org}{Website} \textbar{}
\href{http://github.com/jamesjwills}{GitHub}

\section{Work Experience}\label{work-experience}

\noindent\rule{\textwidth}{0.4pt}

\textbf{Software Developer} \textbar{} Policy Monitor Ltd \textbar{}
2024 - present

\noindent\rule{\textwidth}{0.4pt}

\subsection{CSPM - Cyber Security Product
development}\label{cspm---cyber-security-product-development}

Tech stack: Angular, Java, SQL, MariaDB, LDAP, Apache Tomcat, Maven, AWS
Cloud Services, Figma for UX.

\begin{itemize}
\tightlist
\item
  Product development work encompassing a full-stack product and
  customer management in the cyber security space.
\end{itemize}

\subsection{Diegesis Hub - Timesheet and Invoicing Platform
development}\label{diegesis-hub---timesheet-and-invoicing-platform-development}

Tech stack: Angular, Java, SQL, UX Design, Data Analytics, AWS Cloud
Services, Figma for UX.

\begin{itemize}
\tightlist
\item
  Refactored the data architecture to enable persistent storage and
  historical insights.
\item
  Improved database performance by 10x through query optimisation.
\item
  Designed UX-driven features for project managers.
\item
  Automated monthly analytics reporting, saving time for PMs and senior
  leadership.
\item
  Delivered accurate monthly invoices and timesheets across teams.
\item
  Rewritten user documentation to support wider adoption and future
  development.
\end{itemize}

\subsection{GenAI Code Conversion
Tool}\label{genai-code-conversion-tool}

Tech stack: OpenROAD 4GL, C\#, HuggingFace, Python, InstructLAB.

\begin{itemize}
\tightlist
\item
  Contributed to a generative AI code conversion tool to translate
  OpenROAD 4GL to C\#.
\end{itemize}

\subsection{AI Document Assembly Tool}\label{ai-document-assembly-tool}

Tech stack: Angular, TypeChat, LMStudio, Python.

\begin{itemize}
\tightlist
\item
  Developed a document summarisation app incorporating Microsoft's
  TypeChat NLP framework with an Angular frontend and Python backend.
\end{itemize}

\subsection{Infrascale Integration}\label{infrascale-integration}

Tech stack: Java, Camel DSL, SOAP APIs.

\begin{itemize}
\tightlist
\item
  Developed a Java based integration interface with Infrascale backup
  services, including error handling, validation design and secure API
  standards.
\end{itemize}

\subsection{2iC - Device Communication in Low Latency
Networks}\label{ic---device-communication-in-low-latency-networks}

Tech stack: Java, Networking, Node-RED, Lean Service Architecture.

\begin{itemize}
\tightlist
\item
  Developed service board functionality to fetch remote platforms for
  their ``Mission Control'' product.
\item
  Updated training documentation to reflect updates in product
  development.
\end{itemize}

\subsection{Training}\label{training}

\begin{itemize}
\tightlist
\item
  Diegesis training in Ingres, DBA, SQL, ABF and OpenROAD 4GL.
\item
  Member of company Special Interest Group training in UX/UI.
\end{itemize}

\section{Skills and Certifications}\label{skills-and-certifications}

Java, C\#, SQL, Angular, Camel DSL, SOAP and REST APIs, Lean Service
Architecture and Microservice Architecture, Generative AI (Oracle Cloud
Infrastructure 2024 Generative AI Certified Professional), Cloud
Technologies (AWS Solutions Architect), Quantum Computing (IBM Quantum
Business Foundations).

\section{Previous Employment}\label{previous-employment}

\noindent\rule{\textwidth}{0.4pt}

\textbf{Lecturer in Philosophy} \textbar{} Pembroke College, Oxford
\textbar{} 2022 - 2023

\noindent\rule{\textwidth}{0.4pt}

Taught advanced courses in formal philosophy (logic, metaphysics). Wrote
and delivered lectures for the Advanced Philosophy of Physics course.

\noindent\rule{\textwidth}{0.4pt}

\textbf{Graduate Teaching Assistant} \textbar{} London School of
Economics \textbar{} 2017 - 2022

\noindent\rule{\textwidth}{0.4pt}

Led undergraduate classes in introductory philosophy, philosophy and
foundations of physics and the philosophy and foundations of finance.

\noindent\rule{\textwidth}{0.4pt}

\textbf{Teacher of Mathematics and Physics} \textbar{} Bedford School
\textbar{} 2015 - 2017

\noindent\rule{\textwidth}{0.4pt}

Taught classes in GCSE, IB HL and A-level Further Mathematics.

\section{Education}\label{education}

\noindent\rule{\textwidth}{0.4pt}

\textbf{Java Software Engineer} \textbar{} Firebrand bootcamp \textbar{}
2023 - 2024

\noindent\rule{\textwidth}{0.4pt}

Took examined courses in: Certiport IT Java Specialist, Microsoft Azure
Fundamentals AZ-900, Microsoft Developer Associate AZ-204.

\noindent\rule{\textwidth}{0.4pt}

\textbf{PhD Philosophy} \textbar{} London School of Economics \textbar{}
2017 - 2022

\noindent\rule{\textwidth}{0.4pt}

Thesis: ``Identity and Indistinguishability in Thermal Physics''.
Published articles in leading philosophy journals. Presented my research
at leading international philosophy conferences. For publications, and
other writing, see my website.

\noindent\rule{\textwidth}{0.4pt}

\textbf{MPhysPhil Physics and Philosophy (2.i)} \textbar{} Brasenose
College, Oxford \textbar{} 2011 - 2015

\noindent\rule{\textwidth}{0.4pt}

Academic Exhibition. Led the Astronomy Society's initiative to restore
their abandoned telescope and dome.

\section{Volunteering}\label{volunteering}

\noindent\rule{\textwidth}{0.4pt}

\textbf{Treasurer} \textbar{} The Order of Malta Volunteer \textbar{}
2020 - 2024

\noindent\rule{\textwidth}{0.4pt}

Managed the charity's activities with the Chairman, I took
responsibility for the charity's finances, budgets and annual accounts
in collaboration with the Trustees.

\noindent\rule{\textwidth}{0.4pt}

\textbf{Quantum Computing Course Leader} \textbar{} Diegesis Ltd
\textbar{} 2025 - present

\noindent\rule{\textwidth}{0.4pt}

Designing and leading a course on Quantum Computing for the benefit of
employees' CPD, following IBM's \emph{Quantum Business Foundations}
course.

\end{document}
